\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2024-01-05 forwards-and-backwards.tex
no more overfull hboxes

Now consider
\begin{multline}
	\label{square of F-integral}
    &\IE\Big[
	\Big(\int_s^t\big\langle\rho_\epsilon*|f|(x) \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
\eta_u^N(dx)\big\rangle du\Big)^2\Big]
\\
    &\hspace{4em}=
2\IE\Big[
	\int_s^t\big\langle\rho_\epsilon*|f|(x) \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
\eta_u^N(dx)\big\rangle 
    \\&\hspace{8em}
	\int_u^t\big\langle \rho_\epsilon*|f|(x)\big|F\big(\rho_\epsilon*\eta_r^N(x)\big)\big|,
\eta_r^N(dx)\big\rangle dr
du\Big].
\end{multline}
Since $F$ is polynomial, we use the approach
of Corollary~\ref{alternative form moment bounds}, the tower 
property, and 
Lemma~\ref{bounds on moments}, to bound this
in terms of sums of terms of the form
\[
\IE\Big[\int_s^t(t-u)\int\rho_\epsilon*|f|(x)\rho_\epsilon*\eta_u^N(x)^jdx
\int\rho_\epsilon*|f|(y)\rho_\epsilon*\eta_u^N(y)^kdydu\Big].
\]
Now observe that, again using Lemma~\ref{bounds on moments}, 
since for nonnegative $a$ and $b$, $a^j b^k \le a^{j+k} + b^{j+k}$,
\begin{multline*}
	\IE\left[	\int\int\rho_\epsilon*|f|(x)\rho_\epsilon*\eta_u^N(x)^j
	\rho_\epsilon*|f|(y)\rho_\epsilon*\eta_u^N(y)^k dx dy\right]
	\\
	\leq
	\IE\left[\int\int\|f\|_\infty\rho_\epsilon*\eta_u^N(x)^{j+k}
	\rho_\epsilon*|f|(y)
	dx dy
+
	\int\int
	\rho_\epsilon*|f|(x)
	\|f\|_\infty
	\rho_\epsilon*\eta_u^N(y)^{j+k}
	dx dy \right]
	\\ \leq C\int |f|(x)dx.
\end{multline*}
Thus the quantity~(\ref{square of F-integral}) 
is bounded by $C(t-s)^2$ for a new constant $C$ which we can 
take to be independent of $s$, $t$ and $\epsilon$. Markov's inequality 
then gives
\[
\IP\Big[\|f\|_\infty\int_s^t
\big\langle \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
\eta_u^N(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
\leq C\frac{(t-s)^2}{\nu^2}.
\]
A union bound gives that
\begin{equation}
\label{union bound}
\IP\Big[\max_i\|f\|_\infty\int_{t_{i-1}}^{t_i}
\big\langle \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
\eta_u^N(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
\leq C\frac{T\delta}{\nu^2}.
\end{equation}
Now using Markov's inequality, we can choose $K$ so that
\[
\IP\Big[\|\Delta f\|_\infty\, \sup_{0\leq t\leq T} \langle 1,\eta_t^N\rangle 
>K\Big]<\frac{\nu}{3}, 
\]
and so choosing $\delta$ so that $K\delta<\nu/3$ in this 
expression and $C\delta<\nu^3/3T$ in~(\ref{union bound}),
combining with~(\ref{martingale term to zero}), the result follows.
\end{proof}

@@

$\lim_{\epsilon\to 0, \theta\to\infty}
\widehat{\epsilon}(\delta,\epsilon,\theta)=0$. 

@@

@@

We now turn to the identification of the limit points of the sequence 
$\big\{\big(\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$.
We would like to show that any limit point solves~\eqref{target equation in local convergence}
in the limit, i.e.,
\begin{equation}\label{eqn:target PDE weak form}
    \langle f(x), \varphi(t,x)dx \rangle
    =
    \int_0^t
        \Big\langle
        \frac{1}{2}\Delta f(x) + f(x) F(\varphi(s,x))
        ,
        \varphi(s,x) dx
        \Big\rangle
    ds .
\end{equation}
Since 
$\langle f, \rho_\epsilon*\eta_t^N(x)dx\rangle=
\langle \rho_\epsilon*f(x), \eta_t^N(dx)\rangle$,
and the limit is deterministic,
this will follow if we can show that each of the terms in the semimartingale
decomposition~(\ref{eqn:eta_martingale}),
with the test function $f$ replaced by $\rho_\epsilon*f(\cdot)$,
converges to the corresponding term in~\eqref{eqn:target PDE weak form}.

@@

We first note that,
\begin{align*}
    &
\langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(y)), 
\rho_\epsilon * \eta_s(y) dy \rangle 
-\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle 
\\ 
& = 
\langle \int T_{\epsilon^2} f(y) 
F(\rho_\epsilon * \eta_s(y))\rho_\epsilon(y-w) dy, \eta_s(dw)\rangle - \langle 
T_{\epsilon^2} f(w) F(\rho_\epsilon*\eta_s(w)), \eta_s(dw) \rangle 
\\ 
&= 
\langle \int \big\{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) 
F(\rho_\epsilon*\eta_s(w))\big\} 
\rho_\epsilon(w-y)dy, \eta_s(dw) \rangle.
\end{align*}
Let us denote the integral against $dy$ in the last expression by $I$, that is 
\[ I :=  \int \{ T_{\epsilon^2} f(y) 
F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) 
F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy, \]
and note that $|I|$ is bounded by
\begin{align}
& \int 
\Big\{ |F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)+
F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\Big\} 
\rho_{\epsilon}(w-y)dy
\nonumber \\ &\leq \int \| f\|_{\infty} 
\big|F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))\big| \rho_\epsilon(w-y)dy + 
C \epsilon\|f' \|_\infty |F(\rho_\epsilon*\eta_s(w))|, \label{FirstBoundCT}
\end{align}
where we have used that 
\[
\int |T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w)| p_{\epsilon^2}(w,y)dy
\leq \|f'\|_\infty\int|y-w|p_{\epsilon^2}(w,y)dy.
\]
Now recall that $F$ is a polynomial of degree $n$, and so 
there exist real numbers $b_k$ such
that $F(a)-F(b)= (a-b)\sum_{k=1}^{n-1} b_k a^k b^{n-1-k}$ and so 
\[
|F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|
\leq 
|\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
\sum_{k=1}^{n-1}|b_k|\left(\rho_\epsilon*\eta_s(y)^{n-1}+\rho_\epsilon*\eta_s(w)^{n-1}\right).
\]

@@

The first term in~(\ref{difference in rhos}) gives
\begin{multline*}
\int_\delta^t\IE\Big[\Big\langle\int
	\big\langle\frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
\big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_0(dz)\big\rangle
\\
\big(\rho_\epsilon*\eta_s(y)^k+\rho_\epsilon*\eta_s(w)^k\big)
p_{\epsilon^2}(w,y)dy, \eta_s(dw)\Big\rangle\Big] ds.
\end{multline*}
We ``borrow'' from the exponential term to see that 
$\|y-w\|p_{\epsilon^2}(w,y)\leq C\epsilon p_{2\epsilon^2}(w,y)$
and so bound
this by
\begin{multline}
C\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
\IE\Big[\Big\langle\int\big\langle
\big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_0(dz)
\big\rangle
\\
\big(\rho_\epsilon*\eta_s(y)^k+\rho_\epsilon*\eta_s(w)^k\big)
p_{2\epsilon^2}(w,y)dy, \eta_s(dw)\Big\rangle ds\Big] .
\label{contribution from initial condition terms}
\end{multline}
The four terms in the product are taken separately, according to the
combinations of $w$ and $y$ appearing. First,
\[
\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
\IE\Big[\Big\langle\int\big\langle
p_{2(s+\epsilon^2)}(y,z)   
,\eta_0(dz)
\big\rangle
\rho_\epsilon*\eta_s(y)^k 
p_{2\epsilon^2}(w,y)dy, \eta_s(dw)\Big\rangle  \Big] ds
\]
can be rewritten as
\begin{multline*}
\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
\IE\Big[\int\int\big\langle
p_{2(s+\epsilon^2)}(y,z)  
,\eta_0(dz)
\big\rangle
\rho_\epsilon*\eta_s(y)^k 
p_{\epsilon^2}(x,y) \rho_\epsilon*\eta_s(x) dy dx ds \Big]
\\
\leq
\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
\IE\Big[\int\int\big\langle
p_{2(s+\epsilon^2)}(y,z)  
,\eta_0(dz)
\big\rangle
\big(\rho_\epsilon*\eta_s(y)^{k+1} +\rho_\epsilon*\eta_s(x)^{k+1}\big)
p_{\epsilon^2}(x,y) dy dx \Big] ds,
\end{multline*}
and using Lemma~\ref{bounds on moments} and the tower property, and integrating
with respect to $s$, under our assumptions on $\eta_0$,
this is 
bounded by
\begin{multline*}
C\epsilon \int_\delta^t\frac{1}{\sqrt{s+\epsilon^2}}
\IE\Big[\int\int\big\langle
p_{2(s+\epsilon^2)}(y,z)  
,\eta_0(dz)
\big\rangle
\\
\big(\rho_\epsilon*\eta_0(y)+\rho_\epsilon*\eta_0(y)^{k+1} 
+\rho_\epsilon*\eta_0(x)
+\rho_\epsilon*\eta_0(x)^{k+1}\big)
p_{\epsilon^2}(x,y) dy dx \Big] ds 
\\
\le C'\epsilon\int_\delta^t\frac{1}{(s+\epsilon^2)^{d/2}}ds .
\end{multline*}
For fixed $\delta$, this bound tends to zero as $\epsilon\to 0$.
The term involving 
$ 
\big\langle
p_{2(s+\epsilon^2)}(w,z)   
,\eta_0(dz)
\big\rangle
\rho_\epsilon*\eta_s(w)^k
$ 
is handled similarly.

@@

The approach is standard. We fix $\tau>0$ and, in keeping with
our notation $\rho_\epsilon$, in this subsection, use $\rho_\tau$ to 
denote the symmetric Gaussian kernel with variance parameter $\tau^2$.
Our strategy is to show that, up to an error that tends
to zero as $\tau \to 0$, 
\begin{equation}
\label{approx2}
\int_0^t\int f(z) \rho_\epsilon*\eta_s(z)^2 dz ds
\sim 
\int_0^t\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
\rho_\tau (z-y) (\rho_\epsilon * \eta_s)(y) dz dy ds.
\end{equation}
Analogously, also up to an error that vanishes as $\tau \to 0$,
\begin{equation}
\label{approx3}
\int_0^t\int f(z) \varphi(s,z)^2 dz ds
\sim 
\int_0^t\int \int f(z) \varphi(s,z) 
\rho_\tau (z-y) \varphi(s,y) dz dy ds.
\end{equation}
On the other hand,
weak convergence of $\rho_\epsilon * \eta$ 
(plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\tau(z-y)$) 
gives that 
\begin{equation}
\int_0^t\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
\rho_\tau (z-y) (\rho_\epsilon * \eta_s)(y) dz dy ds
\to \int_0^t \int \int f(z) \varphi(s,z) 
\rho_\tau (z-y) \varphi(s,y) dz dy ds.
\end{equation}
Since $\tau$ is arbitrary, the 
convergence~(\ref{eq:QuadConvergence})
will follow.

@@

    For finite $N$,
    taking $f(\lp)$ of the form \eqref{eqn:test_functions},
    we can use $\psi^N(\lp) = \langle C (1 + u |F(x, \eta)|), \lp(dx, du) \rangle$
    for an appropriate constant $C$.
    For the scaling limit, recall that the test functions $f$ are of the form
    $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$
    with $g(x, u) = 1$ for $u \ge u_0$,
    and consulting~\eqref{eqn:limiting_lookdown_generator},
    we see that most terms in $Af(\lp)$ can be bounded 
    as above by constant multiples of $\langle 1, \eta \rangle$.
    However, the term involving $F$ is, as usual, more troublesome.
    Since $0 \le f(\lp) / g(x, u) \le 1$ for any $(x, u) \in \lp$,
    \begin{align*} % \label{eqn:part_of_psi}
        \big| f(\lp) \sum_{(x, u) \in \lp} F(x, \eta) u \frac{\partial_u g(x, u)}{g(x, u)} \big|
        & \le
        \| \partial_u g \|_\infty \sum_{(x, u) \in \lp} | F(x, \eta) u \ind_{u \le u_0} | \\
        & \le
        \| \partial_u g \|_\infty e^{u_0} \sum_{(x, u) \in \lp} | F(x, \eta) u e^{-u} | .
    \end{align*}
    The first line would be just what we want,
    except that $\psi(\lp)$ cannot depend on $f$, and hence neither on $u_0$.
    So, the second line provides us with the required bound:
    we absorb $\| \partial_u g \|_\infty e^{u_0}$ into $c_f$
    and take $\psi(\lp) = 1 + \langle 1 + F(x, \eta) u e^{-u}, \lp(dx, du) \rangle$.
    % Furthermore, since $F(x, \eta)$ only depends on spatial location, not level,
    % for a given $\lp$ (and hence $\eta = \kappa(\lp)$),
    % $\sup_x |F(x, \eta)|$ is finite.
    % Therefore, we may bound \eqref{eqn:part_of_psi} by
    % $\sup_x |F(x, \eta)| \langle u e^{-u}, \lp \rangle$.
    % To do this we must restrict $\lp$ to lie in the space of measures
    % for which this is finite;
    % however, this is a completely metrizable space
    % \citep[see Condition 2.1 in][]{etheridge/kurtz:2019},
    % and our processes fall in this space (by conditional uniformity).
\end{proof}

@@

It is evident from the description of the process
(or, by differentiating in Definition~\ref{defn:lookdown_mgale})
that
\begin{align} \label{eqn:f_xi_mgale}
\begin{split}
    \langle f, \lp_t^N \rangle
    &=
    \langle f, \lp_0^N \rangle
    + M^f_t
\\ & \qquad {}
    +
    \int_0^t
    \bigg\langle
        c_\theta(x, \eta^N_s)
        \int_u^N \int_{\IR^d}
        \left(
            f(y, u_1) + f(x, u_1) + f(y, u) - f(x, u)
        \right)
        q^m(x, dy, \eta^N_s) du_1 
\\ & \qquad \qquad \qquad \qquad {}
        +
        \left(
            c_\theta(x, \eta^N_s) u^2
            - b_\theta(x, \eta^N_s) u
        \right)
        \frac{d}{du} f(x, u)
    ,
    \lp_s^N(dx, du) \bigg \rangle
    ds ,
\end{split}
\end{align}
where $M^f$ is a martingale
with angle bracket process
\begin{align} \label{eqn:f_xi_qv}
    \begin{split}
    \left\langle M^f \right\rangle_t
    &=
    \int_0^t
    \bigg \langle c_\theta(x, \eta_s^N) \int_u^N \int_{\IR^d}
        \big[ f(y, u_1)^2
\\&\qquad \qquad {}
        + \left( f(x, u_1) + f(y, u) - f(x, u) \right)^2 \big]
    du_1 q^m(x, dy, \eta^N_s)
    ,
    \lp_s^N(dx, du) \bigg \rangle
    ds .
\end{split}\end{align}

@@

\begin{lemma}
    \label{lem:product_tightness}
    Let $\{X^{(n)}\}_{n \ge 1}$ and $\{Y^{(n)}\}_{n \ge 1}$ be sequences of jointly defined
    real-valued processes with c\`adl\`ag paths
    satisfying the conditions of Theorem~\ref{thm:aldous_rebolledo}.
    Then $\{X^{(n)}Y^{(n)}\}_{n \ge 1}$ and $\{X^{(n)} + Y^{(n)}\}_{n \ge 1}$ also
    satisfy the conditions of Theorem~\ref{thm:aldous_rebolledo}.
\end{lemma}

>>>>

Now consider
\begin{multline}
	\label{square of F-integral}
    \IE\Big[
	\Big(\int_s^t\big\langle\rho_\epsilon*|f|(x) \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
\eta_u^N(dx)\big\rangle du\Big)^2\Big]
\\
    =
2\IE\Big[
	\int_s^t\big\langle\rho_\epsilon*|f|(x) \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
\eta_u^N(dx)\big\rangle 
    \\\hspace{8em}
	\times \int_u^t\big\langle \rho_\epsilon*|f|(x)\big|F\big(\rho_\epsilon*\eta_r^N(x)\big)\big|,
\eta_r^N(dx)\big\rangle dr
du\Big].
\end{multline}
Since $F$ is polynomial, we use the approach
of Corollary~\ref{alternative form moment bounds}, the tower 
property, and 
Lemma~\ref{bounds on moments}, to bound this
in terms of sums of terms of the form
\[
\IE\Big[\int_s^t(t-u)\int\rho_\epsilon*|f|(x)\rho_\epsilon*\eta_u^N(x)^jdx
\int\rho_\epsilon*|f|(y)\rho_\epsilon*\eta_u^N(y)^kdydu\Big].
\]
Now observe that, again using Lemma~\ref{bounds on moments}, 
since for nonnegative $a$ and $b$, $a^j b^k \le a^{j+k} + b^{j+k}$,
\begin{multline*}
	\IE\left[	\int\int\rho_\epsilon*|f|(x)\rho_\epsilon*\eta_u^N(x)^j
	\rho_\epsilon*|f|(y)\rho_\epsilon*\eta_u^N(y)^k dx dy\right]
	\\
	\leq
	\IE\left[\int\int\|f\|_\infty\rho_\epsilon*\eta_u^N(x)^{j+k}
	\rho_\epsilon*|f|(y)
	dx dy
+
	\int\int
	\rho_\epsilon*|f|(x)
	\|f\|_\infty
	\rho_\epsilon*\eta_u^N(y)^{j+k}
	dx dy \right]
	\\ \leq C\int |f|(x)dx.
\end{multline*}
Thus the quantity~(\ref{square of F-integral}) 
is bounded by $C(t-s)^2$ for a new constant $C$ which we can 
take to be independent of $s$, $t$ and $\epsilon$. Markov's inequality 
then gives
\[
\IP\Big[\|f\|_\infty\int_s^t
\big\langle \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
\eta_u^N(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
\leq C\frac{(t-s)^2}{\nu^2}.
\]
A union bound gives that
\begin{equation}
\label{union bound}
\IP\Big[\max_i\|f\|_\infty\int_{t_{i-1}}^{t_i}
\big\langle \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
\eta_u^N(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
\leq C\frac{T\delta}{\nu^2}.
\end{equation}
Now using Markov's inequality, we can choose $K$ so that
\[
\IP\Big[\|\Delta f\|_\infty\, \sup_{0\leq t\leq T} \langle 1,\eta_t^N\rangle 
>K\Big]<\frac{\nu}{3}, 
\]
and so choosing $\delta$ so that $K\delta<\nu/3$ in this 
expression and $C\delta<\nu^3/3T$ in~(\ref{union bound}),
combining with~(\ref{martingale term to zero}), the result follows.
\end{proof}

@@

% $\lim_{\epsilon\to 0, \theta\to\infty} \widehat{\epsilon}(\delta,\epsilon,\theta)=0$. 
$\widehat{\epsilon}(\delta,\epsilon,\theta) \to 0$
as $\epsilon\to 0$ and $\theta\to\infty$.

@@

\nonumber \\ &\qquad \qquad {} \hspace{24em} \times

@@

We now turn to the identification of the limit points of the sequence 
of measure-valued processes
$\big(\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}$.
We would like to show that any limit point solves~\eqref{target equation in local convergence}
in the limit, i.e.,
\begin{equation}\label{eqn:target PDE weak form}
    \langle f(x), \varphi(t,x)dx \rangle
    =
    \int_0^t
        \Big\langle
        \frac{1}{2}\Delta f(x) + f(x) F(\varphi(s,x))
        ,
        \varphi(s,x) dx
        \Big\rangle
    ds .
\end{equation}
Since 
$\langle f, \rho_\epsilon*\eta_t^N(x)dx\rangle=
\langle \rho_\epsilon*f(x), \eta_t^N(dx)\rangle$,
and the limit is deterministic,
this will follow if we can show that each of the terms in the semimartingale
decomposition~(\ref{eqn:eta_martingale}),
with the test function $f$ replaced by $\rho_\epsilon*f(\cdot)$,
converges to the corresponding term in~\eqref{eqn:target PDE weak form}.

@@

We first note that,
\begin{align*}
    &
\langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(y)), 
\rho_\epsilon * \eta_s(y) dy \rangle 
-\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle 
\\ 
& = 
\langle \int T_{\epsilon^2} f(y) 
F(\rho_\epsilon * \eta_s(y))\rho_\epsilon(y-w) dy, \eta_s(dw)\rangle - \langle 
T_{\epsilon^2} f(w) F(\rho_\epsilon*\eta_s(w)), \eta_s(dw) \rangle 
\\ 
&= 
\langle \int \big\{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) 
F(\rho_\epsilon*\eta_s(w))\big\} 
\rho_\epsilon(w-y)dy, \eta_s(dw) \rangle.
\end{align*}
Let us denote the integral against $dy$ in the last expression by $I$, that is 
\[ I :=  \int \{ T_{\epsilon^2} f(y) 
F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) 
F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy, \]
and note that $|I|$ is bounded by
\begin{align}
& \int 
\Big\{ |F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)
    \nonumber \\ & \hspace{12em} {} +
F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w)|\Big\} 
\rho_{\epsilon}(w-y)dy
\nonumber \\ &\leq \int \| f\|_{\infty} 
\big|F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))\big| \rho_\epsilon(w-y)dy + 
C \epsilon\|f' \|_\infty |F(\rho_\epsilon*\eta_s(w))|, \label{FirstBoundCT}
\end{align}
where we have used that 
\[
\int |T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w)| p_{\epsilon^2}(w,y)dy
\leq \|f'\|_\infty\int|y-w|p_{\epsilon^2}(w,y)dy.
\]
Now recall that $F$ is a polynomial of degree $n$, and so 
there exist real numbers $b_k$ such
that $F(a)-F(b)= (a-b)\sum_{k=1}^{n-1} b_k a^k b^{n-1-k}$ and so 
\[
|F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|
\leq 
|\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
\sum_{k=1}^{n-1}|b_k|\left(\rho_\epsilon*\eta_s(y)^{n-1}+\rho_\epsilon*\eta_s(w)^{n-1}\right).
\]

@@

The first term in~(\ref{difference in rhos}) gives
\begin{multline*}
\int_\delta^t\IE\Big[\Big\langle\int
	\big\langle\frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
\big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_0(dz)\big\rangle
\\
\big(\rho_\epsilon*\eta_s(y)^k+\rho_\epsilon*\eta_s(w)^k\big)
p_{\epsilon^2}(w,y)dy, \eta_s(dw)\Big\rangle\Big] ds.
\end{multline*}
We ``borrow'' from the exponential term to see that 
$\|y-w\|p_{\epsilon^2}(w,y)\leq C\epsilon p_{2\epsilon^2}(w,y)$
and so bound
this by
\begin{multline}
C\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
\IE\Big[\Big\langle\int\big\langle
\big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_0(dz)
\big\rangle
\\
\big(\rho_\epsilon*\eta_s(y)^k+\rho_\epsilon*\eta_s(w)^k\big)
p_{2\epsilon^2}(w,y)dy, \eta_s(dw)\Big\rangle ds\Big] .
\label{contribution from initial condition terms}
\end{multline}
The four terms in the product are taken separately, according to the
combinations of $w$ and $y$ appearing. First,
\[
\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
\IE\Big[\Big\langle\int\big\langle
p_{2(s+\epsilon^2)}(y,z)   
,\eta_0(dz)
\big\rangle
\rho_\epsilon*\eta_s(y)^k 
p_{2\epsilon^2}(w,y)dy, \eta_s(dw)\Big\rangle  \Big] ds
\]
can be rewritten as
\begin{multline*}
\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
\IE\Big[\int\!\!\int\big\langle
p_{2(s+\epsilon^2)}(y,z)  
,\eta_0(dz)
\big\rangle
\rho_\epsilon*\eta_s(y)^k 
p_{\epsilon^2}(x,y) \rho_\epsilon*\eta_s(x) dy dx ds \Big]
\\
\leq
\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
\IE\Big[\int\!\!\int\big\langle
p_{2(s+\epsilon^2)}(y,z)  
,\eta_0(dz)
\big\rangle
\big(\rho_\epsilon*\eta_s(y)^{k+1} +\rho_\epsilon*\eta_s(x)^{k+1}\big)
p_{\epsilon^2}(x,y) dy dx \Big] ds
\end{multline*}
and using Lemma~\ref{bounds on moments} and the tower property, and integrating
with respect to $s$, under our assumptions on $\eta_0$,
this is 
bounded by
\begin{multline*}
C\epsilon \int_\delta^t\frac{1}{\sqrt{s+\epsilon^2}}
\IE\Big[\int\int\big\langle
p_{2(s+\epsilon^2)}(y,z)  
,\eta_0(dz)
\big\rangle
\\
\big(\rho_\epsilon*\eta_0(y)+\rho_\epsilon*\eta_0(y)^{k+1} 
+\rho_\epsilon*\eta_0(x)
+\rho_\epsilon*\eta_0(x)^{k+1}\big)
p_{\epsilon^2}(x,y) dy dx \Big] ds 
\\
\le C'\epsilon\int_\delta^t\frac{1}{(s+\epsilon^2)^{d/2}}ds .
\end{multline*}
For fixed $\delta$, this bound tends to zero as $\epsilon\to 0$.
The term involving  the product of
$\big\langle p_{2(s+\epsilon^2)}(w,z),\eta_0(dz)\big\rangle$
and $\rho_\epsilon*\eta_s(w)^k$ 
is handled similarly.

@@

The approach is standard. We fix $\tau>0$ and, in keeping with
our notation $\rho_\epsilon$, in this subsection, use $\rho_\tau$ to 
denote the symmetric Gaussian kernel with variance parameter $\tau^2$.
Our strategy is to show that, up to an error that tends
to zero as $\tau \to 0$, 
\begin{equation}
\label{approx2}
\int_0^t\int f(z) \rho_\epsilon*\eta_s(z)^2 dz ds
\sim 
\int_0^t\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
\rho_\tau (z-y) (\rho_\epsilon * \eta_s)(y) dz dy ds.
\end{equation}
Analogously, also up to an error that vanishes as $\tau \to 0$,
\begin{equation}
\label{approx3}
\int_0^t\int f(z) \varphi(s,z)^2 dz ds
\sim 
\int_0^t\int \int f(z) \varphi(s,z) 
\rho_\tau (z-y) \varphi(s,y) dz dy ds.
\end{equation}
On the other hand,
weak convergence of $\rho_\epsilon * \eta$ 
(plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\tau(z-y)$) 
gives that 
\begin{align*}
&
\int_0^t\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
\rho_\tau (z-y) (\rho_\epsilon * \eta_s)(y) dz dy ds
\\ & \qquad
\to \int_0^t \int \int f(z) \varphi(s,z) 
\rho_\tau (z-y) \varphi(s,y) dz dy ds.
\end{align*}
Since $\tau$ is arbitrary, the 
convergence~(\ref{eq:QuadConvergence})
will follow.

@@

    For finite $N$,
    if we take $f(\lp)$ to be of the form \eqref{eqn:test_functions},
    we can use $\psi^N(\lp) = \langle C (1 + u |F(x, \eta)|), \lp(dx, du) \rangle$
    for an appropriate constant $C$.
    For the scaling limit, recall that the test functions $f$ are of the form
    $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$
    with $g(x, u) = 1$ for $u \ge u_0$,
    and consulting~\eqref{eqn:limiting_lookdown_generator},
    we see that most terms in $Af(\lp)$ can be bounded 
    as above by constant multiples of $\langle 1, \eta \rangle$.
    However, the term involving $F$ is, as usual, more troublesome.
    Since $0 \le f(\lp) / g(x, u) \le 1$ for any $(x, u) \in \lp$,
    \begin{align*} % \label{eqn:part_of_psi}
        \big| f(\lp) \sum_{(x, u) \in \lp} F(x, \eta) u \frac{\partial_u g(x, u)}{g(x, u)} \big|
        & \le
        \| \partial_u g \|_\infty \sum_{(x, u) \in \lp} | F(x, \eta) u \ind_{u \le u_0} | \\
        & \le
        \| \partial_u g \|_\infty e^{u_0} \sum_{(x, u) \in \lp} | F(x, \eta) u e^{-u} | .
    \end{align*}
    The first line would be just what we want,
    except that $\psi(\lp)$ cannot depend on $f$, and hence neither on $u_0$.
    So, the second line provides us with the required bound:
    we absorb $\| \partial_u g \|_\infty e^{u_0}$ into $c_f$
    and take $\psi(\lp) = 1 + \langle 1 + F(x, \eta) u e^{-u}, \lp(dx, du) \rangle$.
    % Furthermore, since $F(x, \eta)$ only depends on spatial location, not level,
    % for a given $\lp$ (and hence $\eta = \kappa(\lp)$),
    % $\sup_x |F(x, \eta)|$ is finite.
    % Therefore, we may bound \eqref{eqn:part_of_psi} by
    % $\sup_x |F(x, \eta)| \langle u e^{-u}, \lp \rangle$.
    % To do this we must restrict $\lp$ to lie in the space of measures
    % for which this is finite;
    % however, this is a completely metrizable space
    % \citep[see Condition 2.1 in][]{etheridge/kurtz:2019},
    % and our processes fall in this space (by conditional uniformity).
\end{proof}

@@

It is evident from the description of the process
(or, by differentiating in Definition~\ref{defn:lookdown_mgale})
that
\begin{align} \label{eqn:f_xi_mgale}
\begin{split}
    &\langle f, \lp_t^N \rangle
    =
    \langle f, \lp_0^N \rangle
    + M^f_t
\\ & {}
    +
    \int_0^t
    \bigg\langle
        c_\theta(x, \eta^N_s)
        \int_u^N \int_{\IR^d}
        \left(
            f(y, u_1) + f(x, u_1) + f(y, u) - f(x, u)
        \right)
        q^m(x, dy, \eta^N_s) du_1 
\\ & \qquad \qquad \qquad \qquad {}
        +
        \left(
            c_\theta(x, \eta^N_s) u^2
            - b_\theta(x, \eta^N_s) u
        \right)
        \frac{d}{du} f(x, u)
    ,
    \lp_s^N(dx, du) \bigg \rangle
    ds ,
\end{split}
\end{align}
where $M^f$ is a martingale
with angle bracket process
\begin{align} \label{eqn:f_xi_qv}
    \begin{split}
    \left\langle M^f \right\rangle_t
    &=
    \int_0^t
    \bigg \langle c_\theta(x, \eta_s^N) \int_u^N \int_{\IR^d}
        \big[ f(y, u_1)^2
\\&\qquad \qquad {}
        + \left( f(x, u_1) + f(y, u) - f(x, u) \right)^2 \big]
    du_1 q^m(x, dy, \eta^N_s)
    ,
    \lp_s^N(dx, du) \bigg \rangle
    ds .
\end{split}\end{align}

@@

\begin{lemma}
    \label{lem:product_tightness}
    Let $\{X^{(n)}\}_{n \ge 1}$ and $\{Y^{(n)}\}_{n \ge 1}$ be sequences of jointly defined
    real-valued processes with c\`adl\`ag paths
    satisfying the conditions of Theorem~\ref{thm:aldous_rebolledo}.

    Then $\{X^{(n)}Y^{(n)}\}_{n \ge 1}$ and $\{X^{(n)} + Y^{(n)}\}_{n \ge 1}$ also
    satisfy the conditions of Theorem~\ref{thm:aldous_rebolledo}.
\end{lemma}
